Open-source landscape for 3D CSEM modelling

### 2020-10-13 manuscript/Manuscript.tex
Incorporating new resistivity figure.

% ADDRESSES
\address{
  \footnotemark[1]TU Delft, Building 23, Stevinweg 1 / PO-box 5048, 2628 CN Delft (NL);\\
  \footnotemark[2]Leibniz Institut for Applied Geophysics, Stilleweg 2, 30655 Hannover (DE);\\
  \footnotemark[3]Barcelona Supercomputing Center (BSC), Nexus II Building c/Jordi Girona, 29, 08034 Barcelona (ES);\\
  \footnotemark[4]University of California Berkeley, Department of Statistics (USA).\\
  E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org};\\
  \textbf{Keywords}: CSEM, Open-Source, 3D modelling, FV, FE.
}
% AUTHORS
\author{%
  Dieter Werthmüller\footnotemark[1],          % orcid: 0000-0002-8575-2484
  Raphael Rochlitz\footnotemark[2],            % orcid: 0000-0002-5132-916X
  Octavio Castillo-Reyes\footnotemark[3], and  % orcid: 0000-0003-4271-5015
  Lindsey Heagy\footnotemark[4]                % orcid: 0000-0002-1551-5926
}

@@

\newpage
\itodo{\hfill$\Downarrow$\hfill$\Downarrow$\hfill List of things ToDo, Notes, etc\hfill$\Downarrow$\hfill$\Downarrow$\hfill~}
\begin{itemize}
    \item Notes on orthography: As we submit to GJI it should be British English. But I settled on discretize with a «z». My dictionary says that discreti{\color{red}\bfseries z}e is AE and discreti{\color{red}\bfseries s}e is BE, but that «z» is also used in BE in mathematical contexts. Is that fine or any other opinions?
    \imycom[LJH]{discretize is good with me}
    \item Regarding submission, {\color{red}\bfseries please let me know}:
      \begin{itemize}
        \item If you think the \textbf{order of authors} should be different. The last thing we want in this collaboration is that someone feels unhappy about that: \itodo{No comment from RR; OCR said OK, LJH: +1 looks good to me :)}
        \item If you have \textbf{another manuscript under revision with GJI}. When submitting to GJI one has to indicate when you have other manuscripts currently under review with GJI: \itodo{No comments from Raphael; Octavio, No from Lindsey}
        \item For the submission I will create a \textbf{new repository on swung-research}. The idea is to make a single, new commit with everything (without the git history, for various reasons). Please let me know if you would prefer to commit your files yourself as a PR instead.
        \imycom[OCR]{I have no problem with showing the entire history of the repo (in some way it could justify the way of working collaboratively that is discussed in the abstract), but I would also agree to create a new repo.
        \imycom[DW]{This is actually a good idea, if everyone is up for it. I think we should have a quick call before submitting, and discuss these little points so everyone is happy.}
        \imycom[LJH]{+1, fine by me to transfer the whole repo over with git history (either way is fine by me) }
        }
        \item \textbf{Wanted and not wanted reviewers:} Let me know if you have any names for these. I do not have any \emph{not wanted}, but I do have a few I will put on the \emph{wanted} list, mainly people I would be interested to have their feedback and that have knowledge about 3D modelling:
          \begin{itemize}
            \item Kerry Key (domain knowledge with \texttt{MARE3DEM}, also experience with open-sourcing with \texttt{MARE2DEM}); \itodo{RR and QCR and LJH agreed}
            \item Rune Mittet (domain knowledge; he will know what SBLwiz actually does, so it would be very interesting to have his feedback);
            \item Dimitry Avdeev and Ralph-Uwe Börner (they both did extensive 3D code overview/review papers in 2005 and 2010, respectively, and it would be interesting to get their feedback). \itodo{RR and QCR agreed}
          \end{itemize}
      \end{itemize}
    \item  {\color{red}\bfseries Everyone: Please ensure that the tables have the correct info:}
      \begin{enumerate}
          \item machine info;
          \item runtime;
          \item memory;
          \item nproc;
          \item dof.
      \end{enumerate}
    I got all the info out of the ".nc" files, so make sure you wrote the correct info into the nc-files. Further notes:
      \begin{description}
        \item[runtime] Should only include the wall time (or elapsed real time, \href{https://en.wikipedia.org/wiki/Elapsed_real_time}{wikipedia.org/\-wiki/\-Elapsed\-\_real\-\_time}) of solving the SLE, for ALL frequencies (in \emg3d some frequencies are slower than others, but in any case, we report the sum of all of them); any pre-/postprocessing such as mesh generation or model interpolation can be ignored.
        \item[memory] It should be the maximum memory increase when solving the SLE (again, ignoring any pre-/postprocessing). Again, of all frequencies. In \emg3d some frequencies require more RAM than others (more iterations), but we only report the "worst", the heaviest consumer.
        \item[nproc] Not sure we reached agreement on Slack, but I took no everything in here (threads and (virtual) processes); please note here if you think it should be different.
        \item[dof] Similarly, not sure we reached agreement on Slack. I put it here now for complex value, hence halving the dof of custEM. Again, please write here if we should change it.
    \end{description}
    We could discuss if we should report CPU time instead (hence summing all parallel processes); but I think for the user of interest is the real-world time, how long do I have to wait, so I think it is good as we do it now. (Either way, the reader can make a quick estimation in one or the other direction; important is that we are consistent throughout the paper.)
    \imycom[RR]{Agreed.}
\end{itemize}
\itodo{\hfill$\Uparrow$\hfill$\Uparrow$\hfill List of things ToDo, Notes, etc\hfill$\Uparrow$\hfill$\Uparrow$\hfill~}
\newpage

@@

Controlled-source electromagnetic (CSEM) measurements are a frequently applied method in various geophysical exploration fields, such as geothermal, groundwater, oil and gas, mining, civil engineering, or geo-hazards. Modelling these electromagnetic fields is therefore of great interest to design survey layouts, to understand the measured data, and for inversion purposes. Publications regarding three-dimensional (3D) modelling in electromagnetic methods started to appear as early as the 1970's and 1980's. These early publications were integral equation (IE) methods, having an anomaly embedded within a layered medium, mostly for loop-loop type transient electromagnetic (EM) measurements  \citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}. \cite{B.SEG.88.Ward} assemble many of these solutions in \emph{Electromagnetic Theory for Geophysical Applications}, which is widely viewed as an authoritative publication on electromagnetic geophysics.

@@

In the following, we provide a quick overview of the codes. It is, however, beyond the scope of this article to go into every detail of the different modellers, and we refer to their documentations for more details. An overview comparison of the different codes is given in Table~\ref{tbl:codecomparison}. All codes have in common that they solve Maxwell's equation in its differential form (DE) under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range commonly applied in CSEM. The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.
\imycom[DW]{I took out «the weak formulation of», as it actually doesn't apply to \emg3d. Please make sure that everything stated above («have in common that...») actually applies to your code.
\imycom[RR]{everything fits to custEM}
\imycom[OCR]{ok for petgem}
}
A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations PEC and PMC, which stand for perfect electric conductor and perfect magnetic conductor, respectively. Another abbreviation used in the tables is dof for degree of freedom, which is equivalent to the size of the SLE we are solving. Finally, we use runtime as the wall time or elapsed real time from start to end of solving the SLE; pre- and post-processing (e.g., mesh generation) is not measured. Note that the actual computation or CPU time is therefore much higher than the reported runtime for the codes that run in parallel. Memory refers to the maximum memory increase at any point of solving the SLE.

% Lindsey, I leave the SciPy solvers out. You mention that in practice they are not often used. emg3d can also use those solvers, and then multigrid is used as preconditioner. However, we cite SciPy, and as you say, SimPEG mostly uses PARDISO or MUMPS. To keep it simply I think we can leave SciPy out on the solver side. I mention it in the emg3d-section, if you want you can mention it in the SimPEG section too.
\tabl[bthp]{codecomparison}{Comparison of the four codes under consideration. Note that \emg3d is a solver on its own, while the other codes implement third-package solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.}{
  \centering
  \footnotesize
\begin{tabularx}{\linewidth}{lXXXX}
  \toprule
  %
  & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
       & \href{https://empymod.github.io}{empymod.github.io}
       & \href{http://petgem.bsc.es}{petgem.bsc.es}
       & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  License & GPL-3.0 & Apache-2.0 & BSD 3-Clause & MIT \\
  Installation & \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{pip}
               & \texttt{pip}; \texttt{conda} \\
  Comp. Dom. & frequency \& time & frequency & frequency & frequency \& time \\
  Method & FE & FV & FE & FV \\
  Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
  BC & PEC; PMC & PEC & PEC & PEC; PMC \\
  Solver & \texttt{MUMPS} & \emg3d & \texttt{PETSc}; \texttt{MUMPS} &
           \texttt{PARDISO}; \texttt{MUMPS} \\
  %
  \bottomrule
\end{tabularx}}%
%

@@

% Octavio: We removed the outlook part, we did the same for custEM and emg3d. I hope that is OK.
% Based on the current state of the \petgem project, there are many possibilities to improve or to add additional features. For instance, in the short-term, more modelling routines and support for multi-source set-ups will be implemented. For the long-term, the obvious next step is to move to 3D CSEM data inversion.

\subsection{SimPEG}
\todo{Please condense SimPEG a bit; the other codes use about 190-220 words, SimPEG currently roughly 350.}
\simpeg is a modular toolbox for simulations and gradient based inversions in geophysics. Current functionality includes modelling and inversion capabilities for gravity, magnetics, direct current resistivity, induced polarisation, electromagnetics (time and frequency, controlled and natural sources such as magnetotellurics), and fluid flow (Richards equation). It is a community driven project that aims to support researchers and \mycom[DW]{I added «and practitioners», as I think «support researchers» downplays the fact that \simpeg is used by various companies as well\dots}practitioners by providing a flexible, extensible framework and to facilitate integration of data sets from a variety of geophysical methods, including joint inversions \citep{GJI.20.Astic}, by providing a common interface to each method.

@@

The electromagnetic implementations use a staggered grid finite volume approach where physical properties are discretized at cell centres, fields on cell edges and fluxes on cell faces.
%(for an overview of discretizing Maxwell's equations, we recommend \cite{B.SIAM.14.Haber}).
There are two different discretization strategies implemented for Maxwell's equations: (I) the EB-formulation, which discretizes the electric field ($\vec{e}$) on cell edges and the magnetic flux density ($\vec{b}$) on cell faces, and (II) the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) on cell edges and the current density ($\vec{j}$) on cell faces. The physical properties electrical conductivity / resistivity and magnetic permeability are discretized in both cases at cell centres. Having multiple implementations allows for testing that compares results from each approach, as well as the representation of both electrical and magnetic sources on cylindrically symmetric meshes. \simpeg supports variable magnetic permeability and full-tensor anisotropy for the physical properties.

@@

The full MR3D model consists of $1022 \times 371 \times 1229$ cells, totalling to almost 466 million cells, where each cell has dimensions of 25 by 75 by 5\,m. For the computation the model is upscaled to 515 by 563 by 310 cells, totalling to almost 90 million cells, where each cell has dimensions of 100 by 100 by 20\,m. Both the full model and the upscaled computational model are released openly. The published data set consists of a regular grid of receivers of 20 in eastern direction by 25 in northern direction, 500 receivers in total, with 1\,km spacing located on the irregular seafloor. 45 source-towlines were located on the same grid above each receiver line, 50\,m above the seafloor, with shots every 100\,m. The computed responses for one of the receivers, \texttt{04Rx251a}, are shown in the original paper for the East-West inline-source \texttt{04Tx013a} and the East-West broadside-source \texttt{04Tx014a} (broadside offset of 1\,km). We reproduce the responses for this receiver and corresponding source-lines in our comparison. The $x$-$z$ cross-section of the horizontal resistivity model at the receiver position is shown in Figure~\ref{fig:model-marlim}, together with the receiver and sources positions. All layer have a VTI with $\lambda=\sqrt{2}$, except for the air layer, the seawater, and the salt layer, which are all isotropic.

@@

The responses for all six frequencies and all three electric components are shown in Figure~\ref{fig:results-marlim-responses}, both inline and broadside. The published responses are shown in color (and with markers), and the responses from our codes are shown beneath in grey colours in this overview plot.
%
\plot*{results-marlim-responses}{width=\textwidth}{MR3D comparison between our codes (grey lines) and the published data (coloured lines). The grey lines under the coloured lines are not visible in most areas, meaning they are very similar. However, there are three notable zones, (1) to (3), which are explained further in the text.}
%
Two datasets were published, one containing clean responses, and one where realistic noise was added. For the comparison we use the clean data, but we indicate the chosen noise level by the horizontal line at \num{2e-15}\,V/m. It can be seen that the grey lines are not visible for most parts, which means that the data agree well. However, there are a few notable points where this is not the case, and they are marked with numbers in the figure.
\begin{enumerate}
  \item There are some noticeable differences in the positive offsets of the broadside $E_y$ and $E_z$ components. The differences are related to the bathymetry. And the reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not exactly know what it does internally. See the discussion around Figure~\ref{fig:results-marlim_survey}.
  \item The highest three frequencies became noisy at large offsets for all of our codes (well below any real-world noise level). The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain. This explains their smooth behaviour, without saying anything about their accuracy.
  \item The responses for the $E_y$ component of the inline acquisition line do not agree at all. In the 1D case, the inline $E_y$ component would be zero, and the only response we can measure here come from 3D effects, but they are very low, roughly two orders of magnitude lower than the $E_x$ component. The published responses are not stable either, and therefore any of the responses is as bad as the other. Also, tiniest differences in meshing will have a huge effect here.
\end{enumerate}

Figure~\ref{fig:results-marlim_2published} shows the NRMSDs between the published results and our codes for the three strongest components, the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
%
\plot*{results-marlim_2published}{width=\textwidth}{NRMSDs for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively. Shown are the three frequencies 0.125\,Hz, 0.5\,Hz, and 1.0\,Hz in the top, middle, and bottom row, respectively.}
%
A few general conclusions can be drawn from this figure: In general the NRMSD is roughly 10\,\% or less, particularly for the inline $E_x$ component it is only a few \% or less. In some cases the regular meshes with \emg3d and \simpeg have a smaller NRMSD, such as, e.g., negative offsets in the inline and broadside $E_x$ responses, in some cases the unstructured tetrahedral meshes with \custem and \petgem have a smaller NRMSD, such as, e.g., positive offsets for all broadside $E_y$ responses, and often they have a comparable NRMSD. Some NRMSD have an interesting step-pattern, which is more pronounced for \emg3d and \simpeg than for \custem and \petgem; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}, and will be discussed in more detail with Figure~\ref{fig:results-marlim_survey}.

The importance of the meshing to the result can be seen in Figure~\ref{fig:results-marlim_2ours}, where we compute the NRMSDs between our codes.
%
\plot*{results-marlim_2ours}{width=\textwidth}{NRMSDs, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other. Good visible is that \custem and \petgem produce very similar results, which is due to the fact that they use the same mesh.}
%
The most obvious result in that figure is that \custem and \petgem produce results that are almost identical, their NRMSD is generally below 0.03\,\%. The reason is simple: \custem and \petgem use the exactly same mesh for the computation, the only difference is therefore the solver. As they are so similar we compare \emg3d and \simpeg only to \custem in Figure~\ref{fig:results-marlim_2ours}, as the comparisons to \petgem would look the same. But in general the NRMSDs between our codes look similar as in the comparison with the published results, which is due to the different meshes in use.

The actual differences in meshing is shown in the next two figures, in Figure~\ref{fig:results-marlim_big} for almost the entire computational domain, and in Figure~\ref{fig:results-marlim_survey} a zoom-in to the survey domain, the domain of interest. The dimension of the computational domain varies for the different meshes:
% emg3d:         x = 327 to 454 km; z =  -57 to 83 km
% SimPEG:        x = 288 to 492 km; z = -123 to 41 km
% custEM/PETGEM: as shown in the image (+/- 25 km)
\plot*{results-marlim_big}{width=\textwidth}{Meshes (left column), broadside $E_x$ field (middle column), and broadside $E_y$ field (right column) for a rectilinear mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row). The shown dimensions shows the entire computational domain for the tetrahedra mesh, whereas the entire rectilinear and octree meshes are bigger.}
%
The top rows show the rectilinear mesh of \emg3d, the middle rows the octree mesh of \simpeg, and the bottom rows the tetrahedra mesh of \custem and \petgem. The actual mesh, the $|E_x|$ field, and the $|E_y|$ field are shown in the left, middle, and right columns, respectively.

%
\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a rectilinear mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain (3$\times$ vertical exaggeration).}

The most striking point of these mesh comparison plots is that, while the overall fields are similar and particularly the responses at receiver locations are the same, the fields can vary quite a lot in different parts of the model. At, e.g., two kilometres below the seafloor there are already significant changes visible, purely due to meshing. This is an important insight that has to be taken into account when interpreting inversion results.

The required runtime and memory to compute the shown MR3D responses for the four codes are listed in Table~\ref{tbl:comp-marlim}. The memory requirement varies from $0.5-520\,$GiB, and the runtime from roughly 7\,min to 1h\,23\,min, where the codes were run on very different machines from servers to supercomuters (see Table \ref{tbl:machines}) and use between 1 and 96 processes in parallel).

%
\tabl[bthp]{comp-marlim}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}{
  \centering
\begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
  \toprule
  %
       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
  \midrule
  %
  \custem & 64 &  872 & 230.1 & 1918106 \\ % dof: 3836212 / 2 (Real+Imag -> Complex)
  \emg3d  &  1 & 1200 &   0.5 & 5998992 \\
  \petgem & 96 &  524 & 175.4 & 1918106 \\
  \simpeg &  4 &  422 &  12.8 &  720146 \\ % nprocs: 1*4 threads
  %
  \bottomrule
\end{tabular}}%
%

>>>>

% ADDRESSES
\address{
  \footnotemark[1]TU Delft, Building 23, Stevinweg 1 / PO-box 5048, 2628 CN Delft (NL);\\
  \footnotemark[2]Leibniz Institute for Applied Geophysics, Stilleweg 2, 30655 Hannover (DE);\\
  \footnotemark[3]Barcelona Supercomputing Center (BSC), Nexus II Building c/Jordi Girona, 29, 08034 Barcelona (ES);\\
  \footnotemark[4]University of California Berkeley, Department of Statistics (USA).\\
  E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org};\\
  \textbf{Keywords}: CSEM, Open-Source, 3D modelling, FV, FE.
}
% AUTHORS
\author{%
  Dieter Werthmüller\footnotemark[1],          % orcid: 0000-0002-8575-2484
  Raphael Rochlitz\footnotemark[2],            % orcid: 0000-0002-5132-916X
  Octavio Castillo-Reyes\footnotemark[3], and  % orcid: 0000-0003-4271-5015
  Lindsey Heagy\footnotemark[4]                % orcid: 0000-0002-1551-5926
}

@@

\newpage
\subsection*{Discussed items re manuscript}
\begin{itemize}
  \item Orthography: BE for GJI; using discretize.
  \item Author order is fine by everyone.
  \item Everyone is responsible that the info of their codes is correct (machine info, runtime, memory, dof, etc) and agrees with the info in the \texttt{*.nc}-files.
  \item The runtime in the table is real-world time. So actual computation time is roughly `nprocs x runtime`; also, nprocs includes processes and threads.
  \item Regarding submission:
    \begin{description}
      \item[Current submission] RR, OCR, LH have no submission with GJI currently.
      \item[History] We will keep all git history.
      \item[Repo] \href{https://github.com/swung-research/3d-csem-open-source-landscape/}{github.com/swung-research/3d-csem-open-source-landscape}.
      \item[Suggested reviewers] We suggest the following reviewers, mainly because they have the relevant experience and it would be interesting for us to have their feedback: \emph{Kerry Key} (domain knowledge as developer of \texttt{MARE3DEM}); \emph{Rune Mittet} (domain knowledge; he will know what SBLwiz actually does); \emph{Dimitry Avdeev} and \emph{Ralph-Uwe Börner} (both did extensive 3D code overview/review papers in 2005 and 2010, respectively).
    \end{description}
\end{itemize}

@@

Controlled-source electromagnetic (CSEM) measurements are a frequently applied method in various geophysical exploration fields, such as geothermal, groundwater, oil and gas, mining, civil engineering, or geohazards. Modelling these electromagnetic fields is therefore of great interest to design survey layouts, to understand the measured data, and for inversion purposes. Publications regarding three-dimensional (3D) modelling in electromagnetic methods started to appear as early as the 1970's and 1980's. These early publications were integral equation (IE) methods, having an anomaly embedded within a layered medium, mostly for loop-loop type transient electromagnetic (EM) measurements  \citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}. \cite{B.SEG.88.Ward} assemble many of these solutions in \emph{Electromagnetic Theory for Geophysical Applications}, which is widely viewed as an authoritative publication on electromagnetic geophysics.

@@

In the following, we provide a quick overview of the codes. It is, however, beyond the scope of this article to go into every detail of the different modellers, and we refer to their documentations for more details. An overview comparison of the different codes is given in Table~\ref{tbl:codecomparison}. All codes have in common that they solve Maxwell's equation in its differential form (DE) under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range commonly applied in CSEM. The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.

A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations \emph{PEC} and \emph{PMC}, which stand for perfect electric conductor and perfect magnetic conductor, respectively. Another abbreviation used in the tables is \emph{dof} for degree of freedom, which is equivalent to the size of the SLE we are solving. Finally, we use \emph{runtime} as the wall time or elapsed real-world time from start to end of solving the SLE; pre- and post-processing (e.g., mesh generation) is not measured. Note that the actual computation time or CPU time is therefore much higher than the reported runtime for the codes that run in parallel, with an upper limit of \#Procs$\times$Runtime. Memory refers to the maximum memory increase at any point of solving the SLE.

% Lindsey, I leave the SciPy solvers out. You mention that in practice they are not often used. emg3d can also use those solvers, and then multigrid is used as preconditioner. However, we cite SciPy, and as you say, SimPEG mostly uses PARDISO or MUMPS. To keep it simply I think we can leave SciPy out on the solver side. I mention it in the emg3d-section, if you want you can mention it in the SimPEG section too.
\tabl[bthp]{codecomparison}{Comparison of the four codes under consideration. Note that \emg3d is a solver on its own, while the other codes implement third-package solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.}{
  \centering
  \footnotesize
\begin{tabularx}{\linewidth}{lXXXX}
  \toprule
  %
  & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
       & \href{https://empymod.github.io}{empymod.github.io}
       & \href{http://petgem.bsc.es}{petgem.bsc.es}
       & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  License & GPL-3.0 & Apache-2.0 & BSD-3-Clause & MIT \\
  Installation & \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{pip}
               & \texttt{pip}; \texttt{conda} \\
  Comp. Dom. & frequency \& time & frequency & frequency & frequency \& time \\
  Method & FE & FV & FE & FV \\
  Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
  BC & PEC; PMC & PEC & PEC & PEC; PMC \\
  Solver & \texttt{MUMPS} & \emg3d & \texttt{PETSc}; \texttt{MUMPS} &
           \texttt{PARDISO}; \texttt{MUMPS} \\
  %
  \bottomrule
\end{tabularx}}%
%

@@

\subsection{SimPEG}

\todo{Please condense SimPEG a bit; the other codes use about 190-220 words, SimPEG currently roughly 350.}
\simpeg is a modular toolbox for simulations and gradient based inversions in geophysics. Current functionality includes modelling and inversion capabilities for gravity, magnetics, direct current resistivity, induced polarisation, electromagnetics (time and frequency, controlled and natural sources such as magnetotellurics), and fluid flow (Richards equation). It is a community driven project that aims to support researchers and \mycom[DW]{I added «and practitioners», as I think «support researchers» downplays the fact that \simpeg is used by various companies as well\dots}practitioners by providing a flexible, extensible framework and to facilitate integration of data sets from a variety of geophysical methods, including joint inversions \citep{GJI.20.Astic}, by providing a common interface to each method.

@@

The electromagnetic implementations use a staggered grid finite volume approach where physical properties are discretized at cell centres, fields on cell edges and fluxes on cell faces. There are two different discretization strategies implemented for Maxwell's equations: (I) the EB-formulation, which discretizes the electric field ($\vec{e}$) on cell edges and the magnetic flux density ($\vec{b}$) on cell faces, and (II) the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) on cell edges and the current density ($\vec{j}$) on cell faces. The physical properties electrical conductivity / resistivity and magnetic permeability are discretized in both cases at cell centres. Having multiple implementations allows for testing that compares results from each approach, as well as the representation of both electrical and magnetic sources on cylindrically symmetric meshes. \simpeg supports variable magnetic permeability and full-tensor anisotropy for the physical properties.

@@

The full MR3D model consists of $1022 \times 371 \times 1229$ cells, totalling to almost 466 million cells, where each cell has dimensions of 25 by 75 by 5\,m. The model was upscaled for the computation to 515 by 563 by 310 cells, totalling to almost 90 million cells, where each cell has dimensions of 100 by 100 by 20\,m. Both the full model and the upscaled computational model are released openly. The published data set consists of a regular grid of receivers of 20 in eastern direction by 25 in northern direction, 500 receivers in total, with 1\,km spacing located on the irregular seafloor. 45 source-towlines were located on the same grid above each receiver line, 50\,m above the seafloor, with shots every 100\,m. The computed responses for one of the receivers, \texttt{04Rx251a}, are shown in the original publication for the East-West inline-source \texttt{04Tx013a} and the East-West broadside-source \texttt{04Tx014a} (broadside offset of 1\,km). We reproduce the responses for this receiver and corresponding source-lines in our comparison. The $x$-$z$ cross-section of the horizontal resistivity model at the receiver position is shown in Figure~\ref{fig:model-marlim}, together with the receiver and sources positions. All layer have a VTI with $\lambda=\sqrt{2}$, except for the air layer, the seawater, and the salt layer, which are all isotropic.

@@

The responses for all six frequencies and all three electric components are shown in Figure~\ref{fig:results-marlim-responses}, both inline and broadside. The published responses are shown in colour with markers for the frequency, and the responses from our codes are shown beneath in grey colours in this overview plot.
%
\plot*{results-marlim-responses}{width=\textwidth}{MR3D comparison between our codes (grey lines) and the published data (coloured lines). The grey lines under the coloured lines are not visible in most areas, meaning that they are very similar. However, there are three notable zones, (1) to (3), which are explained further in the text.}
%
Two data-sets were published, one containing clean responses, and one where realistic noise was added. For the comparison we use the clean data, but we indicate the chosen noise level by the horizontal line at \num{2e-15}\,V/m. It can be seen that the grey lines are not visible for most parts, which means that the data agree well. However, there are a few notable points where this is not the case, and they are marked with numbers in the figure.
\begin{enumerate}
  \item There are some noticeable differences in the positive offsets of the broadside $E_y$ and $E_z$ components, which are related to the bathymetry. The reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not exactly know what it does internally. See the discussion around Figure~\ref{fig:results-marlim_survey}.
  \item The highest three frequencies became noisy at large offsets for all of our codes (well below any real-world noise level). The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain. This explains their smooth behaviour, without saying anything about their accuracy.
  \item The responses for the $E_y$ component of the inline acquisition line do not agree at all. In the 1D case, the inline $E_y$ component would be zero, and the only response we can measure here comes from 3D effects. These responses are very low, roughly two orders of magnitude lower than the $E_x$ component. The published responses are not stable either, and therefore any of the responses is as bad as the other. Also, tiniest differences in meshing will have a huge effect here, as well as the boundary condition of the air-water interface of the published results.
\end{enumerate}

As there is no \emph{true} solution we cannot verify the results, but validate by different results using the NRMSD. It is important to not that not the published results nor any of our results is correct, but the closer they agree with each other the more certain we can be of the outcomes. Figure~\ref{fig:results-marlim_2published} shows the NRMSDs between the published results and our codes for the three strongest components, the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
%
\plot*{results-marlim_2published}{width=\textwidth}{NRMSDs for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively. Shown are the three frequencies 0.125\,Hz, 0.5\,Hz, and 1.0\,Hz in the top, middle, and bottom row, respectively.}
%
A few general conclusions can be drawn from this figure: In general the NRMSD is roughly 10\,\% or less. In some cases the regular meshes with \emg3d and \simpeg have a smaller NRMSD, such as, e.g., for negative offsets in the inline and broadside $E_x$ responses, and in some cases the unstructured tetrahedral meshes with \custem and \petgem have a smaller NRMSD, such as, e.g., for positive offsets for all broadside $E_y$ responses, and often they have a comparable NRMSD. Some NRMSDs have an interesting step-pattern, which is more pronounced for \emg3d and \simpeg than for \custem and \petgem; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}, and will be discussed in more detail with Figure~\ref{fig:results-marlim_survey}.

The importance of the meshing to the result can be seen in Figure~\ref{fig:results-marlim_2ours}, where we compute the NRMSDs between our codes.
%
\plot*{results-marlim_2ours}{width=\textwidth}{NRMSDs, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other. Good visible is that \custem and \petgem produce very similar results, which is due to the fact that they use the same mesh. This also shows that the biggest impart in 3D forward modelling comes from the discretization.}
%
The most obvious result in that figure is that \custem and \petgem produce results that are almost identical, their NRMSD is generally below 0.03\,\%. The reason is simple: \custem and \petgem use the exactly same mesh for the computation, the only difference is therefore the solver. This exemplifies that the big difference between different codes is the discretization; the solver is important when it comes to runtime and memory, but not for the accuracy of the result. As these two are so similar we compare \emg3d and \simpeg only to \custem in Figure~\ref{fig:results-marlim_2ours}, as the comparisons to \petgem would look the same. But in general the NRMSDs between our codes look similar as in the comparison with the published results, which is due to the different meshes in use.

The actual differences in meshing is shown in the next two figures. Figure~\ref{fig:results-marlim_big} shows on the top row the rectilinear mesh of \emg3d, on the middle row the octree mesh of \simpeg, and on the bottom row the tetrahedral mesh of \custem and \petgem. The actual mesh, the broadside $|E_x|$ field, and the broadside $|E_y|$ field are shown in the left, middle, and right columns, respectively. The extent of the plot includes the entire computational domain for the tetrahedral mesh; the rectilinear and octree mesh extents are larger (rectilinear: $x=327$ to 454\,km, $z=-57$ to 83\,km; octree: $x=288$ to 492\,km, $z=-123$ to 41\,km).
%
\plot*{results-marlim_big}{width=\textwidth}{Meshes (left column), broadside $E_x$ field (middle column), and broadside $E_y$ field (right column) for the rectilinear mesh / \emg3d (top row), octree mesh / \simpeg (middle row), and tetrahedra mesh / \custem \& \petgem (bottom row). The shown dimensions shows the entire computational domain for the tetrahedra mesh, whereas the entire rectilinear and octree meshes are bigger.}
%
This figure is interesting for various points: The differences between the different meshes are very obvious. Particularly the advantage of octree and tetrahedra, which can create huge cells at the boundary to push away the boundary, whereas a rectilinear grid, even though stretched, has to compute many cells far away of the zone of interest. The different boundary condition also play a part, where the top row used PEC, and the other two rows PMC.

Figure~\ref{fig:results-marlim_survey} shows a zoom-in to the survey domain, the domain of interest, which shows how the different codes discretized the zones of interest.
%
\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for the rectilinear mesh / \emg3d (top row), octree mesh / \simpeg (middle row), and tetrahedra mesh / \custem \& \petgem (bottom row) (3$\times$ vertical exaggeration).}
%
The most striking point of these mesh comparison plots is that, while the overall fields are similar and particularly the responses at receiver locations are the same, the fields can vary quite a lot in different parts of the model. E.g., two kilometres below the seafloor there are already significant changes visible, purely due to meshing. This is an important insight that has to be taken into account when interpreting inversion results.
